%% Master CV - Saqif Mohammed
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as the master reference when tailoring role-specific CVs (cv/main_<company>.tex).
%%
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{needspace}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Saqif Mohammed - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Saqif}{Mohammed}
\address{Bengaluru, India (open to GCC relocation)}{}{}
\phone[mobile]{+91~81233~12844}
\email{saqif.mohammad@gmail.com}
\extrainfo{\href{https://www.linkedin.com/in/saqifmohammed}{LinkedIn} {} \textbar {} \href{https://github.com/saqifmohammed}{GitHub} {} \textbar {} \href{https://offersinksa.com}{offersinksa.com}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT  (tailor per role)
% ============================================================

\vspace{6pt}
\small{Early-stage startup operator and product builder with hands-on experience across product, growth, analytics, and AI workflow automation. Track record of shipping 0\,$\to$\,1 products and driving measurable outcomes, including 11x revenue growth and 65k+ app downloads in two months. Independently built and launched OffersInKSA, a live Saudi Arabia deals aggregator. Targeting product, AI-PM, and growth roles in the GCC (Saudi Arabia, UAE); open to visa sponsorship.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Product (0\,$\to$\,1)}: product development, UX/UI decision-making, roadmapping, user research, competitor analysis.

\item \textbf{Growth}: user acquisition, onboarding optimization, retention, K-factor / virality mechanics, funnel analytics, partnership outreach.

\item \textbf{AI \& Automation}: LLM prototyping, prompt engineering, Claude Code, Replit, vibe-coding, n8n, Airtable.

\item \textbf{Analytics}: Google Analytics, MS Clarity, Shopify Analytics, Power BI, Tableau, SQL.

\item \textbf{Tech Stack}: Next.js, PostgreSQL (Neon), Python, Flutter, GitHub Actions, Figma, Notion, HubSpot.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

\needspace{5\baselineskip}
\item{\cventry{2025--2026}{Founders' Office - Product \& Operations}{Tetro}{Bengaluru, India}{}{\vspace{1pt}
Pre-loved iPhone marketplace (Apple-verified); one of 5 founding team members. Joined as Generalist Intern (Jan 2025), progressed to Founders' Office.
\begin{itemize}
    \item Contributed to 11x revenue growth (Rs 8.4L $\to$ Rs 92.7L; 60\%+ YoY) and a 46\% AOV increase by owning pricing strategy, competitive intelligence, and upmarket repositioning.
    \item Built and shipped AI-powered internal tools via vibe-coding (automated invoicing, product listing pipeline, QC workflows) using Claude Code, Replit, and LLM no-code platforms.
    \item Scaled order volume from 35 annual to 64 in 2 months, putting the business on track for a Rs 1.5Cr+ run rate.
    \item Led website UX/UI and tracked customer experience with GA, MS Clarity, and Shopify analytics to fix funnel drop-offs.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2024}{Growth Associate (Internship)}{Wyb}{Bengaluru, India}{}{\vspace{1pt}
Social discovery app, early-stage growth team.
\begin{itemize}
    \item Drove 65,000+ app downloads within 2 months of launch via combined paid and organic acquisition.
    \item Led the college partnership channel (prospected, negotiated, and closed university deals), a primary install driver.
    \item Improved onboarding completion from 65\% to 85\% (+20pp) and drove K-factor to 0.4 with referral and peer-sharing mechanics.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2024}{Business Analyst Intern}{56Secure}{Bengaluru, India}{}{\vspace{1pt}
\begin{itemize}
    \item Built Power BI dashboards and Excel models to surface actionable insights for data-driven decisions.
    \item Segmented the B2C base in HubSpot and launched community sales campaigns that increased conversions.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2023}{Business Development Associate Intern}{Cube}{Bengaluru, India}{}{\vspace{1pt}
VC-backed startup (Peak XV / Sequoia India, Graph Ventures).
\begin{itemize}
    \item Connected 400+ business owners through LinkedIn using Sales Navigator, working closely with the founding team.
\end{itemize}}}

\end{itemize}

% ============================================================
%     INDEPENDENT PROJECTS
% ============================================================

\section{Independent Projects}
\vspace{3pt}
\begin{itemize}

\needspace{4\baselineskip}
\item{\cventry{2025}{OffersInKSA - KSA Deals \& Bank Offers Aggregator}{\href{https://offersinksa.com}{offersinksa.com}}{}{}{\vspace{1pt}
\begin{itemize}
    \item Independently designed, built, and launched a live full-stack platform; 984+ verified offers across Al Rajhi, SNB, Riyad Bank, and 10+ Saudi banks.
    \item Built with Next.js, Neon PostgreSQL, and automated Python pipelines (GitHub Actions) for daily ingestion and deduplication; bilingual (Arabic/English), SEO-optimized for KSA.
\end{itemize}}}

\vspace{3pt}

\needspace{3\baselineskip}
\item{\cventry{2025}{BlurrCam - Mobile Privacy Camera App}{\href{https://github.com/saqifmohammed/blurrcam}{github.com/saqifmohammed/blurrcam}}{}{}{\vspace{1pt}
\begin{itemize}
    \item Built a Flutter mobile app for real-time background blur in camera captures (Flutter SDK, Windows).
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\needspace{3\baselineskip}
\item{\cventry{2021--2024}{BBA, Entrepreneurship \& Business Analytics}{Yenepoya University}{Mangalore, India}{}{\vspace{1pt}
\begin{itemize}
    \item Entrepreneurship Club President (2023-24); organized and led a 2-day business event with 500+ participants.
\end{itemize}}}

\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item English (fluent), Malayalam, Hindi, Kannada, Arabic (beginner - reading/writing).
\end{itemize}

% ============================================================
%     CERTIFICATIONS
% ============================================================

\section{Certifications}
\vspace{1pt}
\begin{itemize}
\item Cisco - Data Analytics Essentials.
\item Cisco - Introduction to Data Science.
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
